Discrete Quantum Theories and Computing

### 2019-04-06 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

Since conventional quantum theory is defined over the continuum of
complex numbers which cannot be identified with unbounded resources,
it is natural to explore alternative versions of quantum theory incorporate
our limitation of distinguishability. Examining the computational
and physical consequences of such frameworks can yield new insights
into the power and capacity of quantum computing. We have described
two types of discrete quantum theories: quantum theories and computing
over finite fields and quantum interval-valued probability measures.

>>>>

Since conventional quantum theory is defined over the continuum of
complex numbers, but each complex number can only be identified with
unbounded resources, it is natural to explore alternative versions
of quantum theory incorporate our limitation of distinguishability.
Two types of discrete quantum theories have been described in this
thesis: quantum theories and computing over finite fields and quantum
interval-valued probability measures. Examining the computational
and physical consequences of such frameworks can yield new insights
into not only the subtle properties of conventional quantum theory
but also the power and capacity of quantum computing.
